Stack Safety as a Security Property

### 2020-07-04 main.tex
Some more notes derived from yesterday's meeting

% BCP idea: contrast intrinsic vs. extrinsic property definition
% Remember to talk about spatial vs temporal safety

While integrity and confidentiality are standard security
properties, applying them in the stack-safety setting raises a novel challenge:
the notion of ``attacker'' changes during execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be protected from {\em its} callees.
We address this challenge by adjusting the integrity and confidentiality
of different stack frames at each call or return transition between functions.\apt{connection to ``attacker'' still vague.}

@@

\leo{TODO: Add citations of mitigation techniques}

@@

>>>>

\bcp{BCP idea: contrast intrinsic vs. extrinsic property definition
     Remember to talk about spatial vs temporal safety}

While integrity and confidentiality are standard security
properties, applying them in the stack-safety setting raises a novel challenge:
the notion of ``attacker'' changes during execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be protected from {\em its} callees.
We address this challenge by adjusting the integrity and confidentiality
of different stack frames at each call or return transition between functions.\apt{connection to ``attacker'' still vague.}
\rb{Mention to varying ``accessing power'' of the attacker?
  The notion of attacker changes on certain actions that are not externally
  visible.}

@@

\leo{TODO: Add citations of mitigation techniques}
\rb{And for those techniques, explain how they reflect their motivating
examples. What does each technique do for those examples? How are they
connected to this work?}

\rb{Intuition that the callee can do anything in principle, but the machine will
halt if it does not follow the calling convention, etc.?}

@@

\rb{Notes from meeting:
  \begin{itemize}
  \item Explain how the theory applies to production compilers like GCC and
    LLVM, which aspects are directly applicable, what are the effects of
    alternative calling conventions. Other less charted waters: tail calls,
    coroutines, jumps into supervisor mode.
  \item CHERI and its operation, documentation and practical configurations and
    operation.
  \item Compare and contrast with StkTokens.
  \item Under what circumstances can stack safety exist without an enforcement
    mechanism?
  \item Zeroing out of allocated space inside blessed sequences, eager vs lazy.
    Possibility of blessed alloc and dealloc sequences, which also manipulate SP
    and would not be legal without blessing. In such an extended setting, the
    return sequence would check for matching addresses (it would be nice to have
    testing for this!).
  \end{itemize}
}
